Sparsely Activated Networks

### 2020-11-30 ms.tex
fix README.md
simplify Makefile

\newcommand\figscale{0.15}
\begin{document}
\tdplotsetmaincoords{100}{-70}
\DTLloaddb{keys_values}{results/keys-values.csv}

@@

\begin{figure*}[!t]
	\centering
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-identity-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-relu-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-top-k-absolutes-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-extrema-pool-idx-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-extrema-2-activations-0}}
	\\
	\setcounter{subfigure}{0}
	\subfloat[Identity]{\includegraphics[width=0.2\textwidth]{results/MNIST-identity-2-activations-1}\label{subfig:identity}}
	\subfloat[ReLU]{\includegraphics[width=0.2\textwidth]{results/MNIST-relu-2-activations-0}\label{subfig:relu}}
	\subfloat[top-k absolutes]{\includegraphics[width=0.2\textwidth]{results/MNIST-top-k-absolutes-2-activations-0}\label{subfig:topkabsolutes}}
	\subfloat[Extrema-Pool indices]{\includegraphics[width=0.2\textwidth]{results/MNIST-extrema-pool-idx-2-activations-0}\label{subfig:extremapoolindices}}
	\subfloat[Extrema]{\includegraphics[width=0.2\textwidth]{results/MNIST-extrema-2-activations-0}\label{subfig:extrema}}
	\caption{Visualization of the activation maps of five activation functions (Identity, ReLU, top-k absolutes, Extrema-Pool indices and Extrema) for 1D and 2D input in the top and bottom row respectively.
	The 1D input to the activation functions is denoted with the continuous transparent green line using an example from the UCI dataset.
	The output of each activation function is denoted with the cyan stem lines with blue markers.
	The 2D example depicts only the output of the activation functions using an example from the MNIST dataset.
	}
	\label{fig:activationfunctions}
\end{figure*}

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-signal}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-reconstructed}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-reconstruction-0}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-activations-0}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-similarity-0}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{results/UCI-epilepsy-extrema-2-kernel-0}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-signal}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-reconstructed}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-reconstruction-0}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-activations-0}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-similarity-0}};
			\node[opacity=0, left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{results/UCI-epilepsy-extrema-2-kernel-0}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-reconstruction-1}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-activations-1}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-similarity-1}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{results/UCI-epilepsy-extrema-2-kernel-1}};

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-signal}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-reconstructed}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-reconstruction-0}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-activations-0}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-similarity-0}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{results/MNIST-extrema-2-kernel-0}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-signal}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-reconstructed}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-reconstruction-0}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-activations-0}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-similarity-0}};
			\node[opacity=0, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{results/MNIST-extrema-2-kernel-0}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-reconstruction-1}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-activations-1}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-similarity-1}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{results/MNIST-extrema-2-kernel-1}};

@@

\begin{figure*}[!t]
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-apnea-ecg}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-bidmc}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-bpssrat}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-cebsdb}
	\\
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-ctu-uhb-ctgdb}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-drivedb}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-emgdb}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-mitdb}
	\\
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-noneeg}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-prcp}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-shhpsgdb}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-slpdb}
	\\
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-sufhsdb}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-voiced}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-wrist}
	\includegraphics[width=0.245\textwidth]{results/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-legend}
	\caption{Inverse compression ratio ($CR^{-1}$) vs. normalized reconstruction loss ($\tilde{\mathcal{L}}$) for the $15$ datasets of Physionet for various kernel sizes.
	The five inner plots with the yellow background on the right of each subplot, depict the corresponding kernel for the kernel size that achieved the best $\bar\varphi$.}
	\label{fig:crrl}
\end{figure*}

\begin{figure*}[!t]
	\centering
	\subfloat[Density plot $CR^{-1}$ vs. $\tilde{\mathcal{L}}$]{\includegraphics[width=0.32\textwidth]{results/crrl-density-plot}\label{subfig:crrl_density_plot}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $epochs$]{\includegraphics[width=0.32\textwidth]{results/mean-flithos-validation-epochs}\label{subfig:flithos-epochs}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $m$]{\includegraphics[width=0.32\textwidth]{results/mean-flithos-variable-kernel-size-list}\label{subfig:flithos_m}}
	\caption{Aggregated results of the evaluation of the Physionet databases using the $\bar\varphi$ metric.
	The density plot was created using kernel density estimation with Gaussian kernels and the confidence intervals denote one standard deviation.}
	\label{fig:flithos}
\end{figure*}

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-relu-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-top-k-absolutes-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-extrema-pool-idx-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-extrema-1-kernel-0}

@@

\bibliographystyle{IEEEtran}
\bibliography{ms}

>>>>

\newcommand\figscale{0.15}
\begin{document}
\tdplotsetmaincoords{100}{-70}
\DTLloaddb{keys_values}{tmp/keys-values.csv}

@@

\begin{figure*}[!t]
	\centering
	\subfloat{\includegraphics[width=0.2\textwidth]{tmp/UCI-epilepsy-identity-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{tmp/UCI-epilepsy-relu-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{tmp/UCI-epilepsy-top-k-absolutes-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{tmp/UCI-epilepsy-extrema-pool-idx-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{tmp/UCI-epilepsy-extrema-2-activations-0}}
	\\
	\setcounter{subfigure}{0}
	\subfloat[Identity]{\includegraphics[width=0.2\textwidth]{tmp/MNIST-identity-2-activations-1}\label{subfig:identity}}
	\subfloat[ReLU]{\includegraphics[width=0.2\textwidth]{tmp/MNIST-relu-2-activations-0}\label{subfig:relu}}
	\subfloat[top-k absolutes]{\includegraphics[width=0.2\textwidth]{tmp/MNIST-top-k-absolutes-2-activations-0}\label{subfig:topkabsolutes}}
	\subfloat[Extrema-Pool indices]{\includegraphics[width=0.2\textwidth]{tmp/MNIST-extrema-pool-idx-2-activations-0}\label{subfig:extremapoolindices}}
	\subfloat[Extrema]{\includegraphics[width=0.2\textwidth]{tmp/MNIST-extrema-2-activations-0}\label{subfig:extrema}}
	\caption{Visualization of the activation maps of five activation functions (Identity, ReLU, top-k absolutes, Extrema-Pool indices and Extrema) for 1D and 2D input in the top and bottom row respectively.
	The 1D input to the activation functions is denoted with the continuous transparent green line using an example from the UCI dataset.
	The output of each activation function is denoted with the cyan stem lines with blue markers.
	The 2D example depicts only the output of the activation functions using an example from the MNIST dataset.
	}
	\label{fig:activationfunctions}
\end{figure*}

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-signal}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-reconstructed}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-reconstruction-0}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-activations-0}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-similarity-0}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{tmp/UCI-epilepsy-extrema-2-kernel-0}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-signal}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-reconstructed}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-reconstruction-0}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-activations-0}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-similarity-0}};
			\node[opacity=0, left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{tmp/UCI-epilepsy-extrema-2-kernel-0}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-reconstruction-1}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-activations-1}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{tmp/UCI-epilepsy-extrema-2-similarity-1}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{tmp/UCI-epilepsy-extrema-2-kernel-1}};

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-signal}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-reconstructed}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-reconstruction-0}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-activations-0}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-similarity-0}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{tmp/MNIST-extrema-2-kernel-0}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-signal}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-reconstructed}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-reconstruction-0}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-activations-0}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-similarity-0}};
			\node[opacity=0, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{tmp/MNIST-extrema-2-kernel-0}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-reconstruction-1}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-activations-1}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{tmp/MNIST-extrema-2-similarity-1}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{tmp/MNIST-extrema-2-kernel-1}};

@@

\begin{figure*}[!t]
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-apnea-ecg}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-bidmc}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-bpssrat}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-cebsdb}
	\\
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-ctu-uhb-ctgdb}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-drivedb}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-emgdb}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-mitdb}
	\\
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-noneeg}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-prcp}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-shhpsgdb}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-slpdb}
	\\
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-sufhsdb}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-voiced}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-wrist}
	\includegraphics[width=0.245\textwidth]{tmp/mean-inverse-compression-ratio-vs-mean-reconstruction-loss-variable-kernel-size-list-legend}
	\caption{Inverse compression ratio ($CR^{-1}$) vs. normalized reconstruction loss ($\tilde{\mathcal{L}}$) for the $15$ datasets of Physionet for various kernel sizes.
	The five inner plots with the yellow background on the right of each subplot, depict the corresponding kernel for the kernel size that achieved the best $\bar\varphi$.}
	\label{fig:crrl}
\end{figure*}

\begin{figure*}[!t]
	\centering
	\subfloat[Density plot $CR^{-1}$ vs. $\tilde{\mathcal{L}}$]{\includegraphics[width=0.32\textwidth]{tmp/crrl-density-plot}\label{subfig:crrl_density_plot}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $epochs$]{\includegraphics[width=0.32\textwidth]{tmp/mean-flithos-validation-epochs}\label{subfig:flithos-epochs}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $m$]{\includegraphics[width=0.32\textwidth]{tmp/mean-flithos-variable-kernel-size-list}\label{subfig:flithos_m}}
	\caption{Aggregated results of the evaluation of the Physionet databases using the $\bar\varphi$ metric.
	The density plot was created using kernel density estimation with Gaussian kernels and the confidence intervals denote one standard deviation.}
	\label{fig:flithos}
\end{figure*}

@@

	\includegraphics[width=0.06\textwidth]{tmp/apnea-ecg-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/bidmc-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/bpssrat-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/cebsdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/ctu-uhb-ctgdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/drivedb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/emgdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/mitdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/noneeg-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/prcp-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/shhpsgdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/slpdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/sufhsdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/voiced-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/wrist-relu-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{tmp/apnea-ecg-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/bidmc-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/bpssrat-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/cebsdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/ctu-uhb-ctgdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/drivedb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/emgdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/mitdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/noneeg-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/prcp-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/shhpsgdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/slpdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/sufhsdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/voiced-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/wrist-top-k-absolutes-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{tmp/apnea-ecg-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/bidmc-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/bpssrat-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/cebsdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/ctu-uhb-ctgdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/drivedb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/emgdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/mitdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/noneeg-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/prcp-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/shhpsgdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/slpdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/sufhsdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/voiced-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/wrist-extrema-pool-idx-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{tmp/apnea-ecg-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/bidmc-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/bpssrat-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/cebsdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/ctu-uhb-ctgdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/drivedb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/emgdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/mitdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/noneeg-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/prcp-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/shhpsgdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/slpdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/sufhsdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/voiced-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{tmp/wrist-extrema-1-kernel-0}

@@

\bibliographystyle{IEEEtran}
\bibliography{ms.bib}
